---
title: "Notes9"
author: "Haoran Xu"
date: "2024-11-15"
output:
  pdf_document:
    latex_engine: xelatex
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Why the date is set as Nov 14?

先是用Antonio的"reproducile-paper-repo"模版，创建一个新的repository（Github上），然后再用version control输入这个repository的网址（相当于clone），起名叫my-sample-paper。
然后再创建一个r markdown用From Template创建一个Springer模板。
如果想edit，可以用.tex，


如何create一个presentation的html？
在r markdown创建一个presentation模板，这样的好处是每次汇报的时候直接复制代码就行了。

--> 这样可以万事互联 --> notes, presentations, paper 互相关联

e.g., thoguht: 不再用microsoft anymore, 不再使用任何收费的软件(转向QGIS, )


## LaTeX

如果需要插到文字中，可以用$x + y = z$, 如果不需要插到文字中，可以用
$$
f_x = y_x + stitch
$$
one option:
<!-- $$ -->
<!-- \begin{array}{lc} -->
<!--   x = & 3 // -->
<!--   y = & 2 // -->
<!-- \end{array} -->
<!-- $$ -->


Methods
============

## Spatial Autocorrelation and Map Pattern

Spatial autocorrelation is a condition whereby the value of a variable at one location is correlated with the value(s) of the same variable at one or more proximal locations. A tool widely used to measure spatial autocorrelation is Moran’s coefficient of autocorrelation, or $MC$ for short. In matrix form, $MC$ can be formulated as follows:

\begin{equation} 
\label{eq:1}
MC=\frac{n}{\sum_{i}{\sum_{j}{w_{ij}}}}\frac{x'Wx}{x'x}
\end{equation}

where $x$ is a vector $(n\times1)$ of mean-centered values of a georeferenced variable, and $W$ is a spatial weights matrix of dimensions $(n\times n)$ with elements $w_{ij}$. The elements of the spatial weights matrix take non-zero values if locations $i$ and $j$ are deemed to be spatially proximate in some sense, and 0 otherwise. It can be appreciated that the coefficient is composed to two elements: the variance of the random variable (i.e., $(x'x)/n$) and its spatial autocovariance $\frac{(x'Wx)}{\sum_{i}{\sum_{j}{w_{ij}}}}$. As an alternative, the numerator of the right-hand term of Equation \ref{eq:1} can be expressed as follows:

\begin{equation} 
\label{eq:2}
x'\Big(I - \frac{11'}{n}\Big)W\Big(I - \frac{11'}{n}\Big)x
\end{equation}

with $I$ as the identity matrix of size $n\times n$ and $1$ a conformable vector of ones.

One possible interpretation of spatial autocorrelation is as map pattern. More concretely, the eigenvalues of the following matrix represent the range of possible values of $MC$ given a spatial weights matrix $W$, and the extreme eigenvalues are in fact associated with the minimum and maximum values of $MC$ for the system of relationships represented by $W$:

\begin{equation} 
\label{eq:3}
\Big(I - \frac{11'}{n}\Big)W\Big(I - \frac{11'}{n}\Big)
\end{equation}

A remarkable discovery is that the eigenvectors associated with the eigenvalues of the matrix in Expression \ref{eq:3} represent a catalogue of latent map patterns, each with a level of autocorrelation (as measured by $MC$) given by its corresponding eigenvalue. Furthermore, the patterns represented by the eigenvectors are orthogonal by design, and so they furnish $n$ maps that are independent from each other. Since these map patterns depend only on the spatial weights matrix – and not the spatial random variable – they constitute an extensive set of latent map patterns that can be used in regression analysis as filters. This is explained next.


--- 

An example of a figure is Figure \{ref} Figure 1.  # 这个没有写完，需要课后继续完成

```{r echo = FALSE, fig.cap = "\\label{fig:scatterplot}Scatterplot of speed and distance"}
library(ggplot2)
  ggplot(cars) + 
    geom_point(aes(x = speed, y = dist))
```

# 用ggplot举了一个巨nb的例子，大概20行代码，就创造出了一个2x2=4张图不同颜色、不同分布，信息量巨多但很好看的图像。


## Final Deliverable

mock paper: 写具体的段落，做图像(ggplot2)
experimenting with templates





